Boutiques: a flexible framework for automated application integration in computing platforms

### 2017-10-13 boutiquespaper.tex

\author{Tristan Glatard, Tristan Aumentado-Armstrong, Natacha Beck, Pierre Bellec,\\
        Remi Bernard, Sorina Camarasu-Pop, Fr\'ed\'eric Cervenansky, Samir Das, \\
        Rafael Ferreira da Silva, Guillaume Flandin, John Flavin, Pascal Girard, \\
        Krzysztof J. Gorgolewski, Charles G. Guttmann, Gregory Kiar, Nathaniel Kofalt, \\
        Pierre-Olivier Quirion, Pierre Rioux, Marc-\'Etienne Rousseau, Gunnar Schaeffer, Alan C. Evans}
\maketitle

\abstract{Porting applications to execution platforms such as web
  portals and workflow engines is critical to enable their sharing
  among scientific communities and their efficient execution on
  computing infrastructures. However, application porting remains a
  costly human effort that consists of 1)~installing the application
  on the target infrastructure, 2)~describing the application in a
  format compatible with the execution platform, and 3)~generating
  proper user interfaces. Due to the variety of computing platforms,
  application porting efforts are often replicated several times while
  interoperability would save cost and improve the quality of the ported
  applications. We describe \boutiques, a descriptive framework and
  command line utility that allows for automatic import and exchange of
  applications across platforms. \boutiques adopts a rich, flexible
  application description format which relies on Linux container
  environments such as Docker and Singularity to install applications
  across platforms in a lightweight manner. Boutiques is currently used
  by three distinct virtual research platforms, and has been used to
  describe dozens of neuroinformatics tools.}

>>>>

\author{Tristan Glatard, Gregory Kiar, Tristan Aumentado-Armstrong,
  Natacha Beck, Pierre Bellec,\\ Remi Bernard, Sorina Camarasu-Pop,
  Fr\'ed\'eric Cervenansky, Samir Das, \\ Rafael Ferreira da Silva,
  Guillaume Flandin, John Flavin, Pascal Girard, \\ Krzysztof
  J. Gorgolewski, Charles G. Guttmann, Val\'erie Hayot-Sasson,
  Nathaniel Kofalt, \\ Pierre-Olivier Quirion, Pierre Rioux,
  Marc-\'Etienne Rousseau, Gunnar Schaeffer, Alan C. Evans}

\note{greg}{gk's affiliation: Department of Biomedical Engineering, Johns Hopkins University, Baltimore, MD}

\maketitle

\abstract{Porting applications to execution platforms such as web
  portals and workflow engines is critical to enable their sharing
  among scientific communities and their efficient execution on
  computing infrastructures. However, application porting remains a
  costly human effort that consists of 1)~installing the application
  on the target infrastructure, 2)~describing the application in a
  format compatible with the execution platform, and 3)~generating
  proper user interfaces. Due to the variety of computing platforms,
  application porting efforts are often replicated several times while
  interoperability would save cost and improve the quality of the ported
  applications. We describe \boutiques, a descriptive framework and
  command line utility that allows for automatic import and exchange of
  applications across platforms. \boutiques adopts a rich, flexible
  application description format which relies on Linux container
  environments such as Docker and Singularity to install applications
  across platforms in a lightweight manner. \boutiques is currently used
  by three distinct virtual research platforms, and has been used to
  describe dozens of neuroinformatics tools.}
